Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex
Update on Overleaf.

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix. Inner product involves multiplying two matrices by taking dot products of corresponding rows and columns. Gustavson product optimizes memory access by storing one matrix in row-major order and the other in column-major order. Outer product computes the product of all pairs of elements from the input matrices. Our results indicate that inner and Gustavson products perform competitively, while outer product exhibits different characteristics, especially with sparse matrices.

>>>>

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner product, outer product, and Gustavson's method are three different approaches to performing SpGEMM. 
Inner product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer product computes the product of all pairs of elements from the input matrices.
